resevol: an R package for spatially explicit models of pesticide resistance

### 2022-08-01 notebook/ms/ms.Rmd
Begin writing up the second supplemental information

---
title: 'resevol: an R package for spatially explicit models of pesticide resistance
  given evolving pest genomes'
author: |
  | A. Bradley Duthie&#xb9;&#xb2;, et al.
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2]  alexander.duthie@stir.ac.uk, Biological and Environmental Sciences 3A149
  University of Stirling Stirling, FK9 4LA, UK'
output:
  word_document:
    reference_docx: docx_template.docx
  pdf_document:
    toc: no
  html_document: default
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    toc: no
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{RESEVOL, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: resevol.bib
biblio-style: apalike
---

@@

Landscapes are spatially explicit and initialised in one of two ways. 
First, a landscape can be built from the arguments `xdim`, `ydim`, and `farms`. 
These arguments specify the dimensions of the landscape and the number of farms on it.
Contiguous rectangular farms of roughly equal size are generated on the landscape using a splitline algorithm.
Second, a custom landscape can be input using the `terrain` argument, which takes a matrix with elements that include integers 1 to `farms`.
Each value defines a unique farm, but values do not need to be contiguous.
These 'farms' could even model non-farmland (e.g., water, roads), if pesticides and crops on them are invisible to pests (see Supporting Information 2).
This `terrain` customisation therefore allows for a high degree of landscape detail, and offers the potential for modelling real-world landscapes from raster images.
Landscapes are assumed to be a torus, so pests that move off of one edge return on the opposite side of the landscape.

@@

```{r, eval = TRUE}
sim <- run_farm_sim(mine_output = new_network, repro = "asexual", 
                    pesticide_number = 2, pesticide_init = "random", 
                    pesticide_consume = c("T1", "T2"), farms = 9,
                    pesticide_rotation_time = 16, pesticide_rotation_type = 3,
                    pesticide_tolerated_surv = 0, pesticide_per_cell = 1,
                    crop_rotation_time = 16, crop_number = 1, crop_per_cell = 4, 
                    food_consume = 1, reproduction_type = "food_based", 
                    food_needed_surv = 1, food_needed_repr = 1, max_age = 4, 
                    min_age_feed = 0, max_age_feed = 2, min_age_move = 3, 
                    max_age_move = 4, min_age_reproduce = 4, print_gens = FALSE,
                    max_age_reproduce = 4, age_pesticide_threshold = 2, 
                    rand_age = TRUE, move_distance = 2, immigration_rate = 10, 
                    time_steps = 160, print_last = TRUE, xdim = 64, ydim = 64,
                    trait_means = c(0.1, 0.1));
```

>>>>

---
title: 'resevol: an R package for spatially explicit models of pesticide resistance
  given evolving pest genomes'
author: |
  | A. Bradley Duthie&#xb9;&#xb2;, et al.
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2]  alexander.duthie@stir.ac.uk, Biological and Environmental Sciences 3A149
  University of Stirling Stirling, FK9 4LA, UK'
output:
  word_document:
    reference_docx: docx_template.docx
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    toc: no
  pdf_document:
    toc: no
  html_document: default
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{RESEVOL, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: resevol.bib
biblio-style: apalike
---

@@

Landscapes are spatially explicit and initialised in one of two ways. 
First, a landscape can be built from the arguments `xdim`, `ydim`, and `farms`. 
These arguments specify the dimensions of the landscape and the number of farms on it.
Contiguous rectangular farms of roughly equal size are generated on the landscape using a splitline algorithm.
Second, a custom landscape can be input using the `terrain` argument, which takes a matrix with elements that include integers 1 to `farms`.
Each value defines a unique farm, but values do not need to be contiguous.
These 'farms' could even model non-farmland (e.g., water, roads), if pesticides and crops on them are invisible to pests (see Supporting Information 2).
This `terrain` customisation therefore allows for a high degree of landscape detail, and offers the potential for modelling real-world landscapes from raster images.
Edge effects are set using the `land_edge` argument.
Edge options include `"leaky"` (pests disappear from the landscape), `"reflect"` (pests bounce off of the edge), `"sticky"` (pests stick to the edge), or `"torus"` (pests that move off of one edge return on the opposite side of the landscape).

@@

```{r, eval = TRUE}
sim <- run_farm_sim(mine_output = new_network, repro = "asexual", 
                    pesticide_number = 2, pesticide_init = "random", 
                    pesticide_consume = c("T1", "T2"), farms = 9,
                    pesticide_rotation_time = 16, pesticide_rotation_type = 3,
                    pesticide_tolerated_surv = 0, pesticide_per_cell = 1,
                    crop_rotation_time = 16, crop_number = 1, crop_per_cell = 4, 
                    food_consume = 1, reproduction_type = "food_based", 
                    food_needed_surv = 1, food_needed_repr = 1, max_age = 4, 
                    min_age_feed = 0, max_age_feed = 2, min_age_move = 3, 
                    max_age_move = 4, min_age_reproduce = 4, print_gens = FALSE,
                    max_age_reproduce = 4, age_pesticide_threshold = 2, 
                    rand_age = TRUE, move_distance = 2, immigration_rate = 10, 
                    time_steps = 160, print_last = TRUE, xdim = 64, ydim = 64,
                    trait_means = c(0.1, 0.1), land_edge = "torus");
```
